---
title: "FTICR results"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE,
                      collapse = TRUE,
                      warning = FALSE,
                      message = FALSE,
                      comment = "#>"
                      #fig.path = ("markdown-figs/fticr2/")
                      )
```

---

## I. Metabolomics (21T)

<details>   
   <summary>click to expand</summary>


### Van Krevelen Domains
```{r, fig.width=5, fig.height=5}
readd(gg_vankrevelen_domains)
```

---


### Van Krevelen Diagrams

All molecules identified

```{r, fig.width=9, fig.height=5}
readd(gg_vankrevelens)
```

Unique molecules per temperature/CUE

```{r, fig.width=10}
readd(gg_vankrevelen_unique)
```

---

### Relative Abundance

```{r}
readd(gg_relabund_bar)
```


---

### PERMANOVA

```{r}
readd(fticr_permanova) %>% knitr::kable()
```

### PCA
```{r}
readd(gg_pca)
```


  </summary>
</details>


---

## II. Lipidomics (12T)

<details>   
   <summary>click to expand</summary>

### Van Krevelen Domains
```{r, fig.width=5, fig.height=5}
readd(gg_vankrevelen_domains_lipid)
```

---

### Van Krevelen Diagrams

All molecules identified

```{r, fig.width=9, fig.height=5}
readd(gg_vankrevelens_lipid)
```

Unique molecules per temperature/CUE

```{r, fig.width=10}
readd(gg_vankrevelen_unique_lipid)
```

---

### Relative Abundance

```{r}
readd(gg_relabund_bar_lipid)
```

---

### PERMANOVA

```{r}
readd(lipid_permanova) %>% knitr::kable()
```

```{r}
## PCA
# readd(gg_pca)
```

  </summary>
</details>

--- 


## III. Metabolomics (12T)

<details>   
   <summary>click to expand</summary>

### Van Krevelen Domains
```{r, fig.width=5, fig.height=5}
readd(gg_vankrevelen_domains_12T)
```

---

### Van Krevelen Diagrams

All molecules identified

```{r, fig.width=9, fig.height=5}
readd(gg_vankrevelens_12T)
```

Unique molecules per temperature/CUE

```{r, fig.width=10}
readd(gg_vankrevelen_unique_12T)
```

---

### Relative Abundance

```{r}
readd(gg_relabund_bar_12T)
```

---

### PERMANOVA

```{r}
readd(permanova_12T) %>% knitr::kable()
```

```{r}
## PCA
readd(gg_pca_12T)
```

  </summary>
</details>

--- 

---

## Session Info

<details>   
   <summary>click to expand</summary>

Date run: `r Sys.Date()`

```{r}
sessionInfo()
```

</details>   
